True versus apparent shapes of astrophysical bow shocks

### 2015-06-30 papers/Paper1/sec-conic.tex
30/06/15 New advances to conics section.

In this section we will analyze the case where the resultant shape is a conic curve (circle, ellipse, parabola or hyperbola).
These curves are mathematical simple to model and give us a good reference to understand the effects of the projection effects
described in the last section on other bowshocks. Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates thethe given curve is a closed one, i.e
an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary

@@

where:
\begin{align}
\Cos(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 = a - x_0 
\end{align}

@@

\begin{align}
a' = a^2\cos^2 i \pm b^2\sin^2 i \\
\Cos t' = \frac{\Cos(t)}{a\cos i} \\
b' = b
\end{align}

@@

The minimum value of $t$ is such that $1-\frac{b^2}{a^2}\tan^2 i T^2(t_\parallel) =0$, where:

\begin{align}
X'(t_\parallel) = R'_0 \\
\Cot t = \frac{a^2}{b^2}\tan i
\end{align}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

In this section we will analyze the case where the resultant shape  of the bow shock is a conic curve (circle, ellipse, parabola or hyperbola).
These curves are mathematical simple to model and give us a good reference to understand the effects of the projection effects
described in the last section on other bow shocks. The source of the inner wind is located at the origin, and the center of the conic is located at
a distance $x_0$ from the source.
%Instead of the excentricity, we utilize the parameter $\theta_c$ to characterize the different curves, where
%$\tan\theta_c = \frac{b}{a}$,  $b$ and $a$ are the typical parameters of conics. A positive value for $\theta_c$ indicates thethe given curve is a closed one, i.e
%an ellipse, while a negative value indicates that is an hyperbola. %Insert figures if neccesary

@@

where:
\begin{align}
\Cos(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 = a - x_0 \\
a<0 ~ \mathrm{for~hyperbola}
\end{align}

@@

\begin{align}
a' = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2} \\
\Cos t' = \frac{\Cos(t)}{a\cos i} \\
b' = b
\end{align}

@@

\begin{align}
D' = D\cos i \\
R'_0 = a' - (a-R_0)\cos i \\
R'_0 = \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
\end{align}

With $\tan\theta_c\equiv \frac{b}{a}$,  $f(i;\theta_c)\equiv\left(1-\tan^2\theta_c\tan^2i\right)^{1/2}$ and introducing the
radius of curvature $R_c\equiv \frac{b^2}{a}$ we find that:

\begin{align}
\frac{R'_0}{D'}={R_0}{D}\left(1-A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\end{align}

Where $A\equiv \frac{R_c}{R_0}$
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:
